---
title: "Student's Behavior Report"
author: "Brenda Ramirez and Priscila Pena"
date: "DATA 2401"
output: 
  slidy_presentation:
    theme: cosmo
  html_document:
    fig_weight: 3
    fig_width: 4
    highlight: tango
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Introduction

[Student Behavior Data Link](https://www.kaggle.com/datasets/gunapro/student-behavior/data)

This data from Kaggle was collected from various students through a survey. It aims to provide an understanding into student behavior and as current college students we wanted to learn more about what the data has to say about our typical behavior.

## Questions

-   What are the stress levels of students by gender?

-   Is there a relationship between social media usage and their stress level?

-   

## Packages Used

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

## Unfiltered Data

```{r}
data <- read.csv("Student_Behaviour.csv")
glimpse(data)
```

## Data Key Terms

```{r}

```
