---
title: "Student's Behavior Report"
author: "Brenda Ramirez & Priscila Pena"
date: "DATA 2401"
output: 
  slidy_presentation:
    theme: journal
  html_document:
    fig_weight: 3
    fig_width: 4
    highlight: tango
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

## Introduction

[Student Behavior Data Link](https://www.kaggle.com/datasets/gunapro/student-behavior/data)

This data from Kaggle was collected from various students through a survey. It aims to provide an understanding into student behavior and as current college students we wanted to learn more about what the data has to say about our typical behavior.

## Questions

-   What are the stress levels of students by gender?

-   Is there a relationship between social media usage and their stress level?

-   Do students with a low financial status tend to have higher stress levels?

-   Is there a relationship between the type of hobby a student has and their college mark?

-   Is there a relationship between students that like their degree and their willingness to pursue a career out of it?

-   What hobby is the most popular among students?

-   What gender tends to have higher academic marks?

-   Do students who perceive themselves to be in a low financial situation tend to have a part time job?

## Packages Used

```{r echo=TRUE , message=FALSE}
library(tidyverse) #aids in cleaning and presenting data
library(dplyr) #data manipulation
library(ggplot2) #data visualization

```

## Unfiltered Data

```{r}
data <- read.csv("Student_Behaviour.csv")
glimpse(data)
```

## Data Key Terms

Stress Level : perceived stress level of the student

Gender

Social Media & Video : engagement with these platforms

Financial Status : economic background or current financial status of the student

Hobbies : interests of the students

College Mark : grades obtained in their college or university \* since its from another country their grade scale is different

Do you like your degree : opinion on whether they like their degree or not

Willingness to pursue a career based on their degree : a percentage of that likeliness

Salary expectation : future salary expectations

Part-time job : whether or not a student is engaged in one

## Difference in gender data
There are more males in this data set than females
```{r}

data %>% count(Gender)

percentage_data <- data %>% count(Gender) %>% mutate(percentage = round(n/sum(n)*100))

ggplot(percentage_data, aes(x = Gender, y = percentage, fill = Gender)) + geom_bar(stat = "identity") + geom_text(aes(label = paste0(percentage, "%")), 
            position = position_stack(vjust = 0.5), 
            size = 3, 
            color = "black") +
  labs(title = "Gender Distribution",
       x = "Gender",
       y = "Percentage") +
  scale_fill_manual(values = c("Male" = "lightblue", "Female" = "lightpink"))


```


## Random Male sample
```{r}
set.seed(79)
sample_size <- 79

male_sample <- data %>%
  filter(Gender == "Male") %>%
  sample_n(size = sample_size, replace = FALSE) %>%
  select(Gender, Stress.Level)
male_sample

```

## What are the stress levels of students by gender?

```{r}

combined_data <- bind_rows(data %>% filter(Gender == "Female"), male_sample %>% mutate(Gender = "Male_Sample"))
stress_levels_order <- c("Awful", "Bad", "Good", "fabulous")
combined_data$Stress.Level <- factor(combined_data$Stress.Level, levels = stress_levels_order)
combined_data %>%
  mutate(Gender = as.factor(Gender)) %>%
  ggplot(mapping = aes(x = Stress.Level, fill = Gender)) +
  geom_bar(position = "dodge", stat = "count") +
  scale_fill_manual(values = c("Female" = "lightpink", "Male_Sample" = "darkblue")) +
  labs(title = "Stress Level by Gender",
       x = "Stress Level",
       y = "Count")


```

## Is there a relationship between social media usage and their stress level?

```{r}
social_media_order <- c("0 Minute", "1 - 30 Minute","30 - 60 Minute", "1 - 1.30 hour", "1.30 - 2 hour", "More than 2 hour")
stress_levels_order <- c("Awful", "Bad", "Good", "fabulous")

data$Stress.Level <- factor(data$Stress.Level, levels = stress_levels_order)
data$social.medai...video <- factor(data$social.medai...video, levels = social_media_order)

ggplot(data, aes(x = Stress.Level, fill = social.medai...video)) +
  geom_bar(position = "dodge", stat = "count") +
  labs(title = "Relationship between Stress Level and Social Media Usage",
       x = "Stress Level",
       y = "Count") +
  scale_fill_manual(values = c("0 Minute" = "lightblue", 
                               "1 - 30 Minute" = "lightgreen", 
                               "30 - 60 Minute" = "lightpink", 
                               "1 - 1.30 hour" = "darkblue", 
                               "1.30 - 2 hour" = "lightcoral", 
                               "More than 2 hour" = "orange")) +
  facet_wrap(~social.medai...video, scales = "free_y", ncol = 2)

```

## Do students with a low financial status have higher stress levels?

```{r}
ggplot(data, aes(x = Financial.Status, fill = Stress.Level)) +
  geom_bar(stat = "count") +
  labs(title = "Relationship between Financial Status and Stress Level",
       x = "Financial Status",
       y = "Count") +
  scale_fill_manual(values = c("Awful" = "lightblue", "Bad" = "lightgreen", "Good" = "lightpink", "Fabulous" = "darkblue")) +
  facet_wrap(~Stress.Level)

```

## Is there a relationship between the type of hobby a student has and their college mark?

```{r}
ggplot(data, aes(x = hobbies, y = college.mark, fill = hobbies)) +
  geom_boxplot(alpha = 0.5) +  # Use alpha for transparency
  labs(title = "Boxplot of College Marks by Hobbies",
       x = "Hobbies",
       y = "College Marks")
```

## Is there a relationship between students that like their degree and their willingness to pursue a career out of it?

```{r}

ggplot(data, aes(x = Do.you.like.your.degree., fill = willingness.to.pursue.a.career.based.on.their.degree)) +
  geom_bar(position = "dodge", stat = "count") +
  labs(title = "Relationship between Liking Your Degree and Willingness to Pursue a Career",
       x = "Do You Like Your Degree?",
       y = "Count") +
  scale_fill_manual(values = c("0%" = "lightblue", "100%" = "lightgreen", "25%" = "lightpink", "50%" = "lightyellow", "75%" = "lightcoral"), breaks = c("0%", "25%", "50%", "75%", "100%")) +
  facet_wrap(~Do.you.like.your.degree., scales = "free_x", ncol = 1)

```

## What hobby is the most popular among students?

```{r}
percentage_data <- data %>% count(hobbies) %>% mutate(percentage = round(n/sum(n)*100))

ggplot(percentage_data, aes(x = reorder(hobbies, -percentage), y = percentage, fill = hobbies)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_text(aes(label = paste0(percentage, "%")), vjust = -0.5) +
  theme_minimal() +
  labs(title = "Distribution of Hobbies",
       x = "Hobbies",
       y = "Percentage") +
  scale_fill_manual(values = c("lightpink", "darkblue", "lightblue", "violet"))
```

## What gender tends to have higher academic marks?  

```{r}
ggplot(data, aes(x = Gender, y = college.mark, fill = Gender)) + geom_violin() + labs(title = "College Marks by Gender",
       x = "Gender",
       y = "College Marks") +
  scale_fill_manual(values = c("Male" = "lightblue", "Female" = "lightpink")) + coord_flip()

```

## Do students who perceive themselves to be in a low financial situation tend to have a part time job?

```{r}

ggplot(data, aes(x =part.time.job , fill = part.time.job)) +
  geom_bar(position = "dodge", stat = "count") +
  labs(title = "Relationship between Financial Status and Part-Time Job",
       x = "Part-Time Job",
       y = "Count") +
  scale_fill_manual(values = c("Yes" = "lightblue", "No" = "lightcoral")) +
  coord_flip() +
  facet_wrap(~Financial.Status)

```

## Summary

We found a positive relationship between the number of students who like their degrees and their willingness to pursue a career out of it. Women tend to have higher marks than men.

A student's stress levels may not be directly influenced by their gender, their social media use, or their financial status. The type of hobby a student chooses also did not seem to affect the type of academic marks they received. Because they are still students, their financial status does not define if they have a part-time job.

Students come from many distinct backgrounds and can't fit into a one-size-fits-all mold.