---
title: "Student's Behavior Report"
author: "Brenda Ramirez & Priscila Pena"
date: "DATA 2401"
output: 
  slidy_presentation:
    theme: cosmo
  html_document:
    fig_weight: 3
    fig_width: 4
    highlight: tango
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Introduction

[Student Behavior Data Link](https://www.kaggle.com/datasets/gunapro/student-behavior/data)

This data from Kaggle was collected from various students through a survey. It aims to provide an understanding into student behavior and as current college students we wanted to learn more about what the data has to say about our typical behavior.

## Questions

-   What are the stress levels of students by gender?

-   Is there a relationship between social media usage and their stress level?

-   Do students with a low financial status tend to have higher stress levels?

-   Is there a relationship between the type of hobby a student has and their college mark?

-   Is there a relationship between students that like their degree and their willingness to pursue a career out of it?

-   Are there any students in the data set that have a significantly lower salary compared to the rest?

-   What hobby is the most popular among students?

-   What gender tends to have higher academic marks?

-   Do students who perceive themselves to be in a low financial situation tend to have a part time job?

## Packages Used

```{r}
library(tidyverse) #aids in cleaning and presenting data
library(dplyr) #data manipulation
library(ggplot2) #data visualization
```

## Unfiltered Data

```{r}
data <- read.csv("Student_Behaviour.csv")
glimpse(data)
```

## Data Key Terms

Stress Level : perceived stress level of the student

Gender

Social Media & Video : engagement with these platforms

Financial Status : economic background or current financial status of the student

Hobbies : interests of the students

College Mark : grades obtained in their college or university

Do you like your degree : opinion on whether they like their degree or not

Willingness to pursue a career based on their degree : a percentage of that likeliness

Salary expectation : future salary expectations

Part-time job : whether or not a student is engaged in one

## What are the stress levels of students by gender?

```{r}
ggplot(data,
       mapping = aes(x = Gender, y = Stress.Level, fill = Stress.Level)) + 
  geom_col()+coord_flip()
```

## Is there a relationship between social media usage and their stress level?

```{r}

```

## Do students with a low financial status have higher stress levels?

```{r}

```

## Is there a relationship between the type of hobby a student has and their college mark?

```{r}

```

## Is there a relationship between students that like their degree and their willingness to pursue a career out of it?

```{r}

```

## Are there any students in the data set that have a significantly lower salary expectation compared to the rest?

```{r}
data %>% select(salary.expectation) %>% arrange(salary.expectation) %>% head(10)




```

## What hobby is the most popular among students?

```{r}
ggplot(data, aes(x="", y=hobbies, fill=hobbies)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  theme_void()
```
```


## What gender tends to have higher academic marks?

```{r}
library(cowplot)

female <- ggplot(data)+geom_col(aes(x=college.mark,y=college.mark, fill = college.mark))
male <- ggplot(data)+geom_col(aes(x=college.mark,y=college.mark, fill=college.mark))
plot_grid(female, male, labels=c("females", "males"))

```

## Do students who perceive themselves to be in a low financial situation tend to have a part time job?

```{r}

```

## Summary
