---
title: "Student's Behavior Report"
author: "Brenda Ramirez & Priscila Pena"
date: "DATA 2401"
output: 
  slidy_presentation:
    theme: cosmo
  html_document:
    fig_weight: 3
    fig_width: 4
    highlight: tango
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

## Introduction

[Student Behavior Data Link](https://www.kaggle.com/datasets/gunapro/student-behavior/data)

This data from Kaggle was collected from various students through a survey. It aims to provide an understanding into student behavior and as current college students we wanted to learn more about what the data has to say about our typical behavior.

## Questions

-   What are the stress levels of students by gender?

-   Is there a relationship between social media usage and their stress level?

-   Do students with a low financial status tend to have higher stress levels?

-   Is there a relationship between the type of hobby a student has and their college mark?

-   Is there a relationship between students that like their degree and their willingness to pursue a career out of it?

-   What hobby is the most popular among students?

-   What gender tends to have higher academic marks?

-   Do students who perceive themselves to be in a low financial situation tend to have a part time job?

## Packages Used

```{r echo=TRUE , message=FALSE}
library(tidyverse) #aids in cleaning and presenting data
library(dplyr) #data manipulation
library(ggplot2) #data visualization

```

## Unfiltered Data

```{r}
data <- read.csv("Student_Behaviour.csv")
glimpse(data)
```

## Data Key Terms

Stress Level : perceived stress level of the student

Gender

Social Media & Video : engagement with these platforms

Financial Status : economic background or current financial status of the student

Hobbies : interests of the students

College Mark : grades obtained in their college or university \* since its from another country their grade scale is different

Do you like your degree : opinion on whether they like their degree or not

Willingness to pursue a career based on their degree : a percentage of that likeliness

Salary expectation : future salary expectations

Part-time job : whether or not a student is engaged in one

## Work in progress
There are more males in this data set than females
```{r}
data %>% count(Gender)

percentage_data <- data %>% count(Gender) %>% mutate(percentage = round(n/sum(n)*100))

ggplot(percentage_data,aes(x= "", y = n, fill= Gender)) + geom_bar(stat="identity", width=1) + geom_text(aes(label = paste0(percentage, "%")), position = position_stack(vjust = 0.5)) + coord_polar("y", start=0)+
  theme_void() + labs(title = "Percentage of Males and Females in this Data",
       fill = "Gender",
       y = "Percentage") + scale_fill_manual(values = c("Male" = "lightblue", "Female" = "lightpink"))

```


## What are the stress levels of students by gender?

```{r}
data %>% mutate(Gender = as.factor(Gender)) %>% ggplot(mapping = aes(x = Stress.Level, fill= Gender))+ geom_bar(position = "dodge") + scale_fill_manual(values = c("Male" = "lightblue", "Female" = "lightpink"))+ labs(title = "Stress Level by Gender",
       x = "Stress Level",
       y = "Count")

```

## Is there a relationship between social media usage and their stress level?

```{r}

ggplot(data, aes(x = Stress.Level, fill = social.medai...video)) + geom_bar(position = "dodge", stat = "count")+ labs(title ="Relationship between Stress Level and Social Media Usage",
       x = "Stress Level",
       y = "Count") +
  scale_fill_manual(values = c("lightblue", "lightgreen", "lightpink", "lightyellow", "lightcoral", "orange")) 
```

## Do students with a low financial status have higher stress levels?

```{r}

ggplot(data,aes(x = Financial.Status, fill = Stress.Level)) + geom_bar(stat = "count") + labs(title = "Relationship between Financial Status and Stress Level",
       x = "Financial Status",
       y = "Count") +
  scale_fill_manual(values = c("lightblue", "lightgreen", "lightpink", "lightyellow"))
```

## Is there a relationship between the type of hobby a student has and their college mark?

```{r}

ggplot(data, aes(x = hobbies, y = college.mark, color = hobbies)) + geom_jitter(position = position_jitter(width = 0.2, height = 0.2), alpha = 0.5) + labs(title = "Scatter Plot of College Marks by Hobbies",
       x = "Hobbies",
       y = "College Marks") 
```

## Is there a relationship between students that like their degree and their willingness to pursue a career out of it?

```{r}

ggplot(data, aes(x= Do.you.like.your.degree., fill= willingness.to.pursue.a.career.based.on.their.degree)) + geom_bar(position = "dodge", stat = "count") + labs(title = "Relationship between Liking Your Degree and Willingness to Pursue a Career",
       x = "Do You Like Your Degree?",
       y = "Count") +
  scale_fill_manual(values = c("0%" = "lightblue", "100%" = "lightgreen", "25%" = "lightpink", "50%" = "lightyellow", "75%" = "lightcoral"))

```

## What hobby is the most popular among students?

```{r}

percentage_data <- data %>% count(hobbies) %>% mutate(percentage = round(n/sum(n)*100))

ggplot(percentage_data,aes(x= "", y = n, fill= hobbies)) + geom_bar(stat="identity", width=1) + geom_text(aes(label = paste0(percentage, "%")), position = position_stack(vjust = 0.5)) + coord_polar("y", start=0)+
  theme_void() + labs(title = "Distribution of Hobbies",
       fill = "Hobbies",
       y = "Percentage")+ scale_fill_manual(values = c("lightpink", "lightyellow", "lightblue", "violet"))

```

## What gender tends to have higher academic marks?  

```{r}
ggplot(data, aes(x = Gender, y = college.mark, fill = Gender)) + geom_violin() + labs(title = "College Marks by Gender",
       x = "Gender",
       y = "College Marks") +
  scale_fill_manual(values = c("Male" = "lightblue", "Female" = "lightpink"))


```

## Do students who perceive themselves to be in a low financial situation tend to have a part time job?

```{r}



ggplot(data, aes(x =  Financial.Status , fill = part.time.job)) + geom_bar(position = "dodge", stat = "count") + labs(title = "Relationship between Financial Status and Part-Time Job",
       x = "Financial Status",
       y = "Count") + scale_fill_manual(values = c("Yes" = "lightblue", "No" = "lightcoral")) +
  coord_flip() 
  
```

## Summary

students come from many distinct backgrounds and cant be fit into a one size fit all mold.  
