---
title: "Student's Behavior Report"
author: "Brenda Ramirez & Priscila Pena"
date: "DATA 2401"
output: 
  slidy_presentation:
    theme: cosmo
  html_document:
    fig_weight: 3
    fig_width: 4
    highlight: tango
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Introduction

[Student Behavior Data Link](https://www.kaggle.com/datasets/gunapro/student-behavior/data)

This data from Kaggle was collected from various students through a survey. It aims to provide an understanding into student behavior and as current college students we wanted to learn more about what the data has to say about our typical behavior.

## Questions

-   What are the stress levels of students by gender?

-   Is there a relationship between social media usage and their stress level?

-   Do students with a low financial status tend to have higher stress levels?

-   Is there a relationship between the type of hobby a student has and their college mark?

-   Is there a relationship between students that like their degree and their willingness to pursue a career out of it?

-   Are there any students in the data set that have a significantly lower salary compared to the rest?

-   What hobby is the most popular among students?

-   What gender tends to have higher academic marks?

-   Do students who perceive themselves to be in a low financial situation tend to have a part time job?

## Packages Used

```{r}
library(tidyverse) #aids in cleaning and presenting data
library(dplyr) #data manipulation
library(ggplot2) #data visualization
```

## Unfiltered Data

```{r}
data <- read.csv("Student_Behaviour.csv")
glimpse(data)
```

## Data Key Terms

## What are the stress levels of students by gender?
```{r}

```
## Is there a relationship between social media usage and their stress level?
```{r}

```
## Do students with a low financial status have higher stress levels?
```{r}

```
## Is there a relationship between the type of hobby a student has and their college mark?
```{r}

```
## Is there a relationship between students that like their degree and their willingness to pursue a career out of it?
```{r}

```
## Are there any students in the data set that have a significantly lower salary expectation compared to the rest?
```{r}

```
## What hobby is the most popular among students?
```{r}

```
## What gender tends to have higher academic marks?
```{r}

```
## Do students who perceive themselves to be in a low financial situation tend to have a part time job?
```{r}

```
## Summary